Map{R}educe in {MPI} for Large-scale Graph Algorithms

### 2010-06-07 paper/results.tex
git-svn-id: svn+ssh://software-srn.sandia.gov/svn/mapreduce/trunk@632 3fc257bb-8550-0410-81b3-a5c103da83f7

Figure~\ref{f:pr} shows the execution time per PageRank iteration for
R-MAT matrices RMAT-20, RMAT-24 and RMAT-28.  Converging the PageRank
iterations to tolerance $0.002$ requires five or six iterations.
Several R-MAT matrices of each size were generated for the
experiments; the average time over the matrices is reported here.  The
Trilinos implementations show near-perfect strong scaling for RMAT-20
and RMAT-24.  The MR-MPI implementations also demonstrate good strong
scaling.  However, MR-MPI's execution time is at least an order of
magnitude greater than the Trilinos implementation.  This result is
due to two factors: ({\it i}) a higher volume of communication in the
MapReduce implementation (where all edges are communicated in each
iteration), compared to the Trilinos implementation (where only
vertex-based data is communicated), and ({\it ii}) out-of-core
operations in MR-MPI were performed because of the page-size
restriction, while all Trilinos operations were performed in-core.
The benefit of MR-MPI's out-of-core implementation is seen, however,
with the RMAT-28 data set, which could be solved on smaller processor
sets than the Trilinos implementation.  For these experiments, the
Trilinos implementation required 64 processors for the RMAT-28 data
set, since it will not operate on matrices that exceed the aggregate
memory of the processors.

>>>>

Figure~\ref{f:pr} shows the execution time per PageRank iteration for
R-MAT matrices RMAT-20, RMAT-24 and RMAT-28.  Converging the PageRank
iterations to tolerance $0.002$ requires five or six iterations.
Several R-MAT matrices of each size were generated for the
experiments; the average time over the matrices is reported here.  The
Trilinos implementations show near-perfect strong scaling for RMAT-20
and RMAT-24.  The MR-MPI implementations also demonstrate good strong
scaling.  However, MR-MPI's execution time is at least an order of
magnitude greater than the Trilinos implementation.  This result is
due to two factors: ({\it i}) a higher volume of communication in the
MapReduce implementation (which comunicates one datum per graph edge
in each iteration), compared to the Trilinos implementation which only
communicates a volume of data proportional to the number of vertices,
and ({\it ii}) out-of-core operations in MR-MPI were performed because
of the page-size restriction, while all Trilinos operations were
performed in-core.  The benefit of MR-MPI's out-of-core implementation
is seen, however, with the RMAT-28 data set, which could be solved on
smaller processor sets than the Trilinos implementation.  For these
experiments, the Trilinos implementation required 64 processors for
the RMAT-28 data set, since it will not operate on matrices that
exceed the aggregate memory of the processors.
